Automatic Differentiation Accelerates Inference for Partially Observed Markov Processes

### 2024-10-18 paper/si.tex
Updates from Overleaf

\documentclass[9pt,twoside,lineno]{pnas-new-si}

@@

\templatetype{pnassupportinginfo}
\input{macros}
\usepackage{refcount}

@@

\title{Accelerated Inference for Partially Observed Stochastic Processes with Automatic Differentiation}
\author{Kevin Tan, Giles Hooker, Edward L. Ionides}
\correspondingauthor{Corresponding Author name.\\E-mail: kevtan@wharton.upenn.edu}

>>>>

\documentclass[numsec,webpdf,modern,medium,namedate]{oup-authoring-template}

@@

%\templatetype{pnassupportinginfo}
\input{macros}
\usepackage{refcount}

@@

\title{Automatic Differentiation Accelerates Inference for Partially Observed Markov Processes}
\author{Kevin Tan, Giles Hooker, Edward L. Ionides}
\correspondingauthor{Corresponding Author name.\\E-mail: ionides@umich.edu}
